---
title: "Actor Racial Lines - Defining diversity"
author: "SGB"
date: "2023-09-19"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

## About - Actor racial lines dataset

This is an actor dataset with information on actors' racial lines
featured in 780 Hollywood films spanning from 1970 to 2014. This dataset
belongs to a another study used to analyze the representation of races &
ethnicity. For more information visit:
<https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/KERZQY>

## Defining diversity

**Diversity** can be defined as the traits or characteristics of an
individual, group or team.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What are some of the key categories within diversity?

There are different dimensions that we can explore diversity. This could
be physical traits such as age, gender, race/ethnicity, nationality or
having a disability. There are also social traits like culture,
education, career, religion, or even socioeconomical status.

## Why is diversity important?

It's important to include people with all of these characteristics on
the crew so that all members of our global society can be represented,
that means giving a voice to everyone.

```{r cars}
#load packages
library(stringr)
library(dplyr)
library(tidyverse)
library(tibble)
library(ggplot2)

#download actor dataset
actors <- read_tsv('https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/KERZQY/E3ODSJ', n_max = Inf)
View(actors)


```

## Exploring dataset - Different metrics for diversity

**A. Gender**

m = stands for 'male'

f = stands for 'female'

Most people in the dataset are male, meaning more actors than actresses.

```{r}
total <- as.numeric(count(actors))
total
actors %>% count(GENDER, sort = TRUE)
gender_sum <-actors %>% group_by(GENDER) %>% summarize(gender_count = n(), gender_perc = round(n()*100/total,2))
gender_sum
ggplot(gender_sum, aes(x= GENDER, y = gender_perc), weight = gender_perc) + geom_col() +ggtitle('Actors representation by gender')
```

**B. Race/Ethnicity**

b = stands for 'Black'

a = stands for 'East Asian'

i = stands for 'Indigenous'

l = stands for 'Latino'

n = stands for 'Near Eastern'

s = stands for 'South Asian'

p = stands for 'Pacific Islander'

w = stands for 'White'

As expected the most common race in the 'Hollywood' sample is 'White'.

```{r}
#character racial lines general summary
actors %>% count(CHARACTER_RACE, sort = TRUE)
char_race <- actors %>%group_by(CHARACTER_RACE)%>%summarize(char_race_count = n(), char_race_perc = round(n()*100/total,2))
char_race
ggplot(char_race, aes(x=CHARACTER_RACE, y=char_race_perc)) + geom_col() +ggtitle('Actor representation by character race')

#actor racial lines general summary
actors %>% count(ACTOR_RACE, sort = TRUE)
actor_race <- actors%>%group_by(ACTOR_RACE)%>%summarize(actor_count= n(), actor_race_perc = round(n()*100/total,2))
actor_race
ggplot(actor_race, aes(x= ACTOR_RACE, y= actor_race_perc)) + geom_col() +ggtitle('Actor representation by actor race')

#character racial lines gender summary
char_gender_race <- actors %>% group_by(GENDER,CHARACTER_RACE) %>% summarize(char_count =n(), char_race_perc = round(n()*100/total,2))


#actor racial lines gender summary
actor_gender_race <- actors %>% group_by(GENDER,ACTOR_RACE) %>% summarize(actor_count = n(), actor_race_perc = round(n()*100/total,2))

```

**C. Age**

```{r}
#age summary in general
mean(actors$AGE, na.rm = TRUE)
max(actors$AGE, na.rm = TRUE)
min(actors$AGE, na.rm = TRUE)

#age summary by gender
actors %>% group_by(GENDER)%>%summarize(mean_age = round(mean(AGE, na.rm = TRUE),1),median_age = median(AGE,na.rm = TRUE),max_age = max(AGE, na.rm = TRUE), min_age = min(AGE, na.rm = TRUE))

#age summary by character race
actors%>%group_by(CHARACTER_RACE)%>%summarize(mean_age = round(mean(AGE, na.rm = TRUE),1), median_age = median(AGE,na.rm = TRUE), max_age = max(AGE, na.rm = TRUE), min_age = min(AGE, na.rm = TRUE))

ggplot(actors, aes(x=AGE)) + geom_histogram(binwidth = 10) + ggtitle('Age variation histogram')
```

## Reference

@data{DVN/KERZQY_2018, author = {Svaikovsky, Victoria and Meisner, Anne
and Kraicer, Eve and Sims, Matthew}, publisher = {Harvard Dataverse},
title = {{Racial Lines}}, UNF = {UNF:6:/qYtamtOhoREW8pHL1R47A==}, year =
{2018}, version = {V3}, doi = {10.7910/DVN/KERZQY}, url =
{<https://doi.org/10.7910/DVN/KERZQY>}
