---
title: "RMarkdown_title_basics"
output: 
  pdf_document: default
  html_document: default
date: "2023-09-12"
---

# General information

This is a report on a dataset downloaded from the IMDB database. This document will allow users to load and understand the content of this dataset, variables and observations. The use and storage of this Non-Commercial dataset is subject to IMDB's terms and conditions. For more details please visit <https://developer.imdb.com/non-commercial-datasets/>. This dataset is contained in a zipped tab-separated-values (TSV) formatted file in the UTF-8 character set. The first line of each variable contains headers which describes what the column contains.

|                            |                            |
|----------------------------|----------------------------|
| **File name:**             | title.basics.tsv.gz        |
| **File type:**             | tab-seperated-values (TSV) |
| **Delimiter:**             | tab                        |
| **Load/Update Frequency:** | daily                      |

Fields in this dataset are the following:

-   **tconst (string)** - alphanumeric unique identifier of the title

-   **titleType (string)** - the type/format of the title (e.g. movie, short, tvseries, tvepisode, video, etc)

-   **primaryTitle (string)** - the more popular title / the title used by the filmmakers on promotional materials at the point of release.

-   **originalTitle (string)** - original title, in the original langueage.

-   **isAdult (boolean)** - 0: non-adult title, 1: adult title

-   **startYear ( yyyy)** - represents the release year of a title. In the case of TV Series, it is the series start year.

-   **endYear (yyyy)** - TV Series end year. '\\N' for all other title types

-   **runtimeMinutes -** primary runtime of the title, in minutes

-   **genres (string array)** - includes up to three genres associated with the title.

## Loading the Data

```{r setup, inclue=FALSE}
## Script Setup
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
```

```{r}
#Load data
##Loading the dataset
title_basics <- read_tsv('https://datasets.imdbws.com/title.basics.tsv.gz', n_max=Inf)

```

## Data exploration

```{r}
summary(title_basics)

```

## Exploring each field for length and nullability

```{r}
# tconst
max(nchar(title_basics$tconst, keepNA=FALSE))
sum(is.na(title_basics$tconst))

# titleType
max(nchar(title_basics$titleType, keepNA=FALSE))
sum(is.na(title_basics$titleType))

# primaryTitle
max(nchar(title_basics$primaryTitle, keepNA=FALSE))
sum(is.na(title_basics$primaryTitle))

# originalTitle
max(nchar(title_basics$originalTitle, keepNA=FALSE))
sum(is.na(title_basics$originalTitle))

# isAdult
max(nchar(title_basics$isAdult, keepNA=FALSE))
sum(is.na(title_basics$isAdult))

# startYear
max(nchar(title_basics$startYear, keepNA=FALSE))
sum(is.na(title_basics$startYear))

# endYear
max(nchar(title_basics$endYear, keepNA=FALSE))
sum(is.na(title_basics$endYear))

# runtimeMinutes
max(nchar(title_basics$runtimeMinutes, keepNA=FALSE))
sum(is.na(title_basics$runtimeMinutes))

# genres
max(nchar(title_basics$genres, keepNA=FALSE))
sum(is.na(title_basics$genres))
```

## Average number of adressed genres per movie

```{r}
Movie_genres <- str_split(title_basics$genres, ",")
Movie_genres_count <- length(Movie_genres[[1]])

# Average genres per Movie
mean(Movie_genres_count)
```

## Number of tconst falling under the "Documentary" genre

```{r}
genre_documentary <- "Documentary"
count <- title_basics %>%
  filter(str_detect(genres, genre_documentary)) %>%
  nrow()

cat("The genre", genre_documentary, "appears in", count, "rows.")
```

## Number of tconst falling under the "Short" genre

```{r}
genre_short <- "Short"
count <- title_basics %>%
  filter(str_detect(genres, genre_short)) %>%
  nrow()

cat("The genre", genre_short, "appears in", count, "rows.")
```

## Number of tconst falling under the "Romance" genre

```{r}
genre_romance <- "Romance"
count <- title_basics %>%
  filter(str_detect(genres, genre_romance)) %>%
  nrow()

cat("The genre", genre_romance, "appears in", count, "rows.")
```

## Number of tconst falling under the "Comedy" genre

```{r}
genre_comedy <- "Comedy"
count <- title_basics %>%
  filter(str_detect(genres, genre_comedy)) %>%
  nrow()

cat("The genre", genre_comedy, "appears in", count, "rows.")
```

## Number of tconst falling under the "Animation" genre

```{r}
genre_animation <- "Animation"
count <- title_basics %>%
  filter(str_detect(genres, genre_animation)) %>%
  nrow()

cat("The genre", genre_animation, "appears in", count, "rows.")
```

## Number of tconst falling under the "News" genre

```{r}
genre_news <- "News"
count <- title_basics %>%
  filter(str_detect(genres, genre_news)) %>%
  nrow()

cat("The genre", genre_news, "appears in", count, "rows.")
```

## Number of tconst falling under the "Sport" genre

```{r}
genre_sport <- "Sport"
count <- title_basics %>%
  filter(str_detect(genres, genre_sport)) %>%
  nrow()

cat("The genre", genre_sport, "appears in", count, "rows.")
```

## Number of tconst falling under the "Drama" genre

```{r}
genre_drama <- "Drama"
count <- title_basics %>%
  filter(str_detect(genres, genre_drama)) %>%
  nrow()

cat("The genre", genre_drama, "appears in", count, "rows.")
```

## Number of tconst falling under the "Horror" genre

```{r}
genre_horror <- "Horror"
count <- title_basics %>%
  filter(str_detect(genres, genre_horror)) %>%
  nrow()

cat("The genre", genre_horror, "appears in", count, "rows.")
```

## Number of tconst falling under the "Fantasy" genre

```{r}
genre_fantasy <- "Fantasy"
count <- title_basics %>%
  filter(str_detect(genres, genre_fantasy)) %>%
  nrow()

cat("The genre", genre_fantasy, "appears in", count, "rows.")
```

## Number of tconst per startYear

```{r}
ggplot(data = title_basics, aes(x = startYear)) +
  geom_bar(fill = "blue") +
  labs(title = "Number of tconst per Start Year",
       x = "Start year",
       y = "# of tconst")
```
