---
title: "IMDB_dataset_name.basics"
output:
  pdf_document: default
  html_document: default
date: "2023-09-12"
---

## General information

This is a report on a dataset downloaded from the IMDB database. This document will allow users to load and understand the content of this dataset, variables and observations. The use and storage of this Non-Commercial dataset is subject to IMDB's terms and conditions. For more details please visit <https://developer.imdb.com/non-commercial-datasets/>. This dataset is contained in a zipped tab-separated-values (TSV) formatted file in the UTF-8 character set. The first line of each variable contains headers which describes what the column contains.

| **File name:**             | **name.basics.tsv.gz**         |
|----------------------------|--------------------------------|
| **File type:**             | **tab-separated-values (TSV)** |
| **Delimeter:**             | **tab**                        |
| **Load/Update Frequency:** | **daily**                      |

The variables in this dataset are the following:

-   nconst (string) - alphanumeric unique identifier of the name/person

-   primaryName (string)-- name by which the person is most often credited

-   birthYear -- in YYYY format

-   deathYear -- in YYYY format if applicable, else 'NA'

-   primaryProfession (array of strings)-- the top-3 professions of the person

-   knownForTitles (array of tconsts) -- titles the person is known for

# Loading the Data

```{r setup, include=FALSE}
## Script Setup
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
```

```{r input}
## Load Data
### Loading the dataset
name_basics <- read_tsv('https://datasets.imdbws.com/name.basics.tsv.gz',n_max=Inf)

### Converting birthYear to numeric
name_basics$birthYear[!grepl("^\\d+$", name_basics$birthYear)] <- NA
name_basics$birthYear <- as.numeric(name_basics$birthYear)

### Converting deathYear to numeric
name_basics$deathYear[!grepl("^\\d+$", name_basics$deathYear)] <- NA
name_basics$deathYear <- as.numeric(name_basics$deathYear)
```

# Data exploration

```{r,}
summary(name_basics)
```

## Exploring each field for length and nullability

```{r}
# nconst
max(nchar(name_basics$nconst, keepNA=FALSE))
sum(is.na(name_basics$nconst))

# primaryName
max(nchar(name_basics$primaryName, keepNA=FALSE))
sum(is.na(name_basics$primaryName))

# birthYear
max(nchar(name_basics$birthYear, keepNA=FALSE))
sum(is.na(name_basics$birthYear))

# deathYear
max(nchar(name_basics$deathYear, keepNA=FALSE))
sum(is.na(name_basics$deathYear))

# primaryProfession
max(nchar(name_basics$primaryProfession, keepNA=FALSE))
sum(is.na(name_basics$primaryProfession))

# knownforTitles
max(nchar(name_basics$knownForTitles, keepNA=FALSE))
sum(is.na(name_basics$knownForTitles))
```

## Number of primaryProfession per nconst

```{r}
Profession_pieces <- str_split(name_basics$primaryProfession, ",")
Profession_piece_count <- length(Profession_pieces[[1]])

# Average primaryProfessions
mean(Profession_piece_count)
```

## Number of knownforTitles per nconst

```{r}
Titles_pieces <- str_split(name_basics$knownForTitles, ",")
Titles_piece_count <- length(Titles_pieces[[1]])

# Average knownforTitles
mean(Titles_piece_count)
```

## Number of nconst per birthYear

```{r}
count_birthYear <- name_basics %>%
  group_by(birthYear) %>%
  summarize(count = n())
```

## Number of nconst per birthYear

```{r}
count_deathYear <- name_basics %>%
  group_by(deathYear) %>%
  summarize(count = n())
```
